% CREATED BY DAVID FRISK, 2014
\begin{thebibliography}{69}

%\bibitem{Reference} Frisk, D. (2014) A Chalmers University of Technology %Master's thesis template for \LaTeX . Unpublished.

\bibitem{Catell} R. Cattell, 'Scalable SQL and NoSQL data stores', ACM SIGMOD Record, vol. 39, no. 4, p. 12, 2011.

\bibitem{MySQLToNoSQL} A. Schram and K. Anderson, 'MySQL to NoSQL', Proceedings of the 3rd annual conference on Systems, programming, and applications: software for humanity - SPLASH '12, 2012.

\bibitem{Mullins} C. Mullins, Database administration. Upper Saddle River, NJ: Addison-Wesley, 2013.

\bibitem{Peffers} K.  Peffers, T.  Tuunanen, M.  Rothenberger and S.  Chatterjee, 'A Design Science Research Methodology for Information Systems Research', Journal of Management Information Systems, vol. 24, no. 3, pp. 45-77, 2007.

%\bibitem{Moon05} Fusheng Wang, C. Zaniolo, Xin Zhou and H. Moon, 'Version Management and Historical Queries in Digital Libraries', 12th International Symposium on Temporal Representation and Reasoning (TIME'05), pp. 207-209, 2005.

%\bibitem{Moon09} H.J, Moon, C.A, Curino, M, Ham and Zaniolo, Z. PRIMA: Archiving and Querying Historical Data with Evolving Schemas. SIGMOD’09, June 29–July 2, pp. 1019-1022, 2009, Providence, Rhode Island, USA.

%\bibitem{Co-evolutionOfSchemaAndCode} D. Qiu, B. Li and Z. Su, 'An empirical analysis of the co-evolution of schema and code in database applications', Proceedings of the 2013 9th Joint Meeting on Foundations of Software Engineering - ESEC/FSE 2013, pp. 125-135, 2013.

\bibitem{DS} A. R. Hevner, S. T. March and J. Park, “Design Science in Information Systems
Research,” MIS Quartely, vol. 28, no. 1, pp. 75-105, 2004.

%\bibitem{MoonPHD} H. Moon, 'Supporting Schema Evolution in Information Systems and Historical Databases', Ph.D, University of California, 2008.

\bibitem{NoSQLSurvey} Jing Han, Haihong E, Guan Le and Jian Du, 'Survey on NoSQL database', 2011 6th International Conference on Pervasive Computing and Applications, pp. 363-366 2011.

\bibitem{NoSQLDistilled} M. Fowler and P. Sadalage, NoSQL distilled. Boston, Mass.: Addison-Wesley, 2012.

%\bibitem{SchemaEvolutionBib} E. Rahm and P. Bernstein, 'An online bibliography on schema evolution', ACM SIGMOD Record, vol. 35, no. 4, pp. 30-31, 2006.

%\bibitem{Oscar} A. Cleve, M. Gobert, L. Meurice, J. Maes and J. Weber, 'Understanding database schema evolution: A case study', Science of Computer Programming, vol. 97, pp. 113-121, 2015.

%\bibitem{EvolutionNoSQL} S. Schrezinger, M. Klettke and U. Störl, 'Managing Schema Evolution in NoSQL Data Stores', 14th International Symposium on Database Programming Languages (DBPL 2013), pp.  August 30, 2013, Riva del Garda, Trento, Italy.

\bibitem{Brewer} S.  Gilbert and N.  Lynch, 'Brewer's conjecture and the feasibility of consistent, available, partition-tolerant web services', SIGACT News, vol. 33, no. 2, p. 51, 2002.

\bibitem{Abadi} D.  Abadi, 'Consistency Tradeoffs in Modern Distributed Database System Design: CAP is Only Part of the Story', Computer, vol. 45, no. 2, pp. 37-42, 2012.

%\bibitem{JSONData}Z.  Liu, B.  Hammerschmidt and D.  McMahon, 'JSON data management: supporting schema-less development in RDBMS', Proceedings of the 2014 ACM SIGMOD international conference on Management of data - SIGMOD '14, pp. 1247-1258, 2014.

%\bibitem{Codd} E.  Codd, 'A relational model of data for large shared data banks', Commun. ACM, vol. 13, no. 6, pp. 377-387, 1970.

\bibitem{ORM} C.  Ireland, D.  Bowers, M.  Newton and K.  Waugh, 'A Classification of Object-Relational Impedance Mismatch', 2009 First International Confernce on Advances in Databases, Knowledge, and Data Applications, pp. 36-43, 2009.

%\bibitem{DbCrossroad} M.  Indrawan-Santiago, 'Database Research: Are We at a Crossroad? Reflection on NoSQL', 2012 15th International Conference on Network-Based Information Systems, pp. 45-51, 2012.

\bibitem{NoSQLERA} A. Moniruzzaman and S. Akhter Hossain, 'NoSQL Database: New Era of Databases for Big data Analytics - Classification, Characteristics and Comparison', International Journal of Database Theory and Application, vol. 6, no. 4, 2013.

\bibitem{DesignEval} A.  Cleven, P.  Gubler and K.  Hüner, 'Design alternatives for the evaluation of design science research artifacts', Proceedings of the 4th International Conference on Design Science Research in Information Systems and Technology - DESRIST '09, 2009.

\bibitem{isoInternalMetric} International Organization for Standardization, Software engineering - Product quality - Part 3: Internal metrics, Japan, 2002

\bibitem{isoExternalMetric} International Organization for Standardization, Software engineering - Product quality - Part 2: External metrics, Japan, 2002   

\bibitem{dbindex} Db-engines.com, 'DB-Engines Ranking - popularity ranking of database management systems', 2015. [Online]. Available: http://db-engines.com/en/ranking. [Accessed: 26- Mar- 2015].

%\bibitem{elasticBok} Gormley, Clinton, and Zachary Tong. Elasticsearch: The Definitive Guide. Beijing u.a.: O'Reilly et Associates, 2015. Print.

%\bibitem{bigDataData} Schultz, 'Big Data Are, After All, Just Data', Perf. Improv., vol. 53, no. 5, pp. 20-25, 2014.

\bibitem{bigDataWarehouse} K. Krishnan, Data warehousing in the age of big data. Morgan Kaufmann, 2013

\bibitem{bigDataMane} McAfee, A., and Brynjolfsson, E. 'Big Data: The Management Revolution.' Harvard Business Review 90:60–68, 2012.

\bibitem{polyglotms} J.  Sharp, D.  McMurtry, A.  Oakley, M.  Subramanian and H.  Zhang, Data Access for Highly-Scalable Solutions: Using SQL, NoSQL, and Polyglot Persistence. Microsoft patterns \& practices, 2013.

\bibitem{bigDatabigAn}M. Minelli, M. Chambers and A. Dhiraj, Big data, big analytics. Wiley, 2013. 

%\bibitem{lean} Liker, The Toyota way. New York: McGraw-Hill, 2004.

\bibitem{FowlerCI} M. Fowler, M. Foemmel. Continous Integration (2006, May 01). [Online] Available: http://www.martinfowler.com/articles/continuousIntegration.html. 

\bibitem{mysql} Mysql.com, 'MySQL ::  The world's most popular open source database', 2015. [Online]. Available: https://www.mysql.com/. [Accessed: 24- Apr- 2015].

\bibitem{tokudb} Tokutek.com, 'TokuDB® for MySQL | MariaDB vs MySQL | MySQL Performance', 2015. [Online]. Available: http://www.tokutek.com/tokudb-for-mysql/. [Accessed: 24- Apr- 2015].

\bibitem{fractaltree} Tokutek.com, 'Learn About TokuMX™ and TokuDB® Distributions', 2015. [Online]. Available: http://www.tokutek.com/resources/technology/. [Accessed: 22- May- 2015].

%\bibitem{mongodb} Mongodb.org, 'MongoDB', 2015. [Online]. Available: https://www.mongodb.org/. [Accessed: 24- Apr- 2015].

\bibitem{elastic} Elastic.co, 'Elastic · Revealing Insights from Data (Formerly Elasticsearch)', 2015. [Online]. Available: https://www.elastic.co/. [Accessed: 24- Apr- 2015].

\bibitem{CIbook} P. Duvall, S. Matyas and A. Glover, Continuous integration. Upper Saddle River, NJ: Addison-Wesley, 2007.

\bibitem{ESmemory} Elastic.co, 'Limiting Memory Usage', 2015. [Online]. Available: http://www.elastic.co/guide/en/elasticsearch/guide/master/\_limiting\_memory\_usage.html. [Accessed: 07- May- 2015].

\bibitem{10rules} M. Stonebraker and R. Cattell, '10 rules for scalable performance in 'simple operation' datastores', Commun. ACM, vol. 54, no. 6, p. 72, 2011. 

\bibitem{JVM} Docs.oracle.com, 'Java Virtual Machine Technology', 2015. [Online]. Available: http://docs.oracle.com/javase/8/docs/technotes/guides/vm/. [Accessed: 22- May- 2015].

\bibitem{sphinx} Sphinxsearch.com, 'Sphinx | Open Source Search Engine', 2015. [Online]. Available: http://sphinxsearch.com/. [Accessed: 22- May- 2015].

\bibitem{redis} Redis.io, 'Redis', 2015. [Online]. Available: http://redis.io. [Accessed: 22- May- 2015].

\bibitem{storageengine} Dev.mysql.com, 'MySQL :: MySQL 5.1 Reference Manual :: 14 Storage Engines', 2015. [Online]. Available: https://dev.mysql.com/doc/refman/5.1/en/storage-engines.html. [Accessed: 24- May- 2015].

\end{thebibliography}
